TGI-spinal-power

### 2022-05-30 analysis/tgispine_zoib_power-sim.Rmd
modelling using beta distribution instead of truncated normal

@@

@@

# Data to use in simulation
```{r}

# Simulating data function - simulate model estimates (mean & sd) into beta distribution
```{r}
simulate_subj <- function(subid, llim, ulim) {
# trial info
trialN = 12
conditionN = 8
ratingN = 3
# creating simulation data-frame
df <- data.frame(matrix(ncol = 0, nrow = trialN*conditionN*ratingN))
df$id <- rep(subid,trialN*conditionN*ratingN)
df$trialn <- rep(1:trialN,conditionN*ratingN)
df$dermatome <- rep(rep(c(rep("within",trialN*2), rep("across",trialN*2)),2),ratingN)
df$cold_location <- rep(rep(c(rep("dist_rostr",trialN), rep("prox_caud", trialN)),conditionN/2),ratingN)
df$stimuli <- rep(c(rep("tgi",trialN*conditionN/2), rep("non-tgi",trialN*conditionN/2)),ratingN)
df$quality <- c(rep("cold",trialN*conditionN), rep("warm",trialN*conditionN), rep("burn",trialN*conditionN))

# Simulate data here based on means and standard deviations of the above pilot sample
# Cold ratings: simulation
# tgi
w_dr_tgi_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_cold, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(tgi_cold, condition == 'within' & cold_location == 'dist_rostr')[, 6])
w_pc_tgi_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_cold, condition == 'within' & cold_location == 'prox_caud')[, 5], 
    sd=filter(tgi_cold, condition == 'within' & cold_location == 'prox_caud')[, 6])
a_dr_tgi_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_cold, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(tgi_cold, condition == 'across' & cold_location == 'dist_rostr')[, 6])
a_pc_tgi_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_cold, condition == 'across' & cold_location == 'prox_caud')[, 5], 
    sd=filter(tgi_cold, condition == 'across' & cold_location == 'prox_caud')[, 6])
# control
w_dr_cnt_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_cold, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(cnt_cold, condition == 'within' & cold_location == 'dist_rostr')[, 6])
w_pc_cnt_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_cold, condition == 'within' & cold_location == 'prox_caud')[, 5], 
    sd=filter(cnt_cold, condition == 'within' & cold_location == 'prox_caud')[, 6])
a_dr_cnt_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_cold, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(cnt_cold, condition == 'across' & cold_location == 'dist_rostr')[, 6])
a_pc_cnt_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_cold, condition == 'across' & cold_location == 'prox_caud')[, 5], 
    sd=filter(cnt_cold, condition == 'across' & cold_location == 'prox_caud')[, 6])

# Warm ratings: simulation
# tgi
w_dr_tgi_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_warm, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(tgi_warm, condition == 'within' & cold_location == 'dist_rostr')[, 6])
w_pc_tgi_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_warm, condition == 'within' & cold_location == 'prox_caud')[, 5], 
    sd=filter(tgi_warm, condition == 'within' & cold_location == 'prox_caud')[, 6])
a_dr_tgi_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_warm, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(tgi_warm, condition == 'across' & cold_location == 'dist_rostr')[, 6])
a_pc_tgi_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_warm, condition == 'across' & cold_location == 'prox_caud')[, 5], 
    sd=filter(tgi_warm, condition == 'across' & cold_location == 'prox_caud')[, 6])
# control
w_dr_cnt_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_warm, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(cnt_warm, condition == 'within' & cold_location == 'dist_rostr')[, 6])
w_pc_cnt_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_warm, condition == 'within' & cold_location == 'prox_caud')[, 5], 
    sd=filter(cnt_warm, condition == 'within' & cold_location == 'prox_caud')[, 6])
a_dr_cnt_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_warm, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(cnt_warm, condition == 'across' & cold_location == 'dist_rostr')[, 6])
a_pc_cnt_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_warm, condition == 'across' & cold_location == 'prox_caud')[, 5], 
    sd=filter(cnt_warm, condition == 'across' & cold_location == 'prox_caud')[, 6])

# Burning ratings: simulation
# tgi
w_dr_tgi_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_burn, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(tgi_burn, condition == 'within' & cold_location == 'dist_rostr')[, 6])
w_pc_tgi_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_burn, condition == 'within' & cold_location == 'prox_caud')[, 5], 
    sd=filter(tgi_burn, condition == 'within' & cold_location == 'prox_caud')[, 6])
a_dr_tgi_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_burn, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(tgi_burn, condition == 'across' & cold_location == 'dist_rostr')[, 6])
a_pc_tgi_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_burn, condition == 'across' & cold_location == 'prox_caud')[, 5], 
    sd=filter(tgi_burn, condition == 'across' & cold_location == 'prox_caud')[, 6])
# control
w_dr_cnt_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_burn, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(cnt_burn, condition == 'within' & cold_location == 'dist_rostr')[, 6])
w_pc_cnt_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_burn, condition == 'within' & cold_location == 'prox_caud')[, 5], 
    sd=filter(cnt_burn, condition == 'within' & cold_location == 'prox_caud')[, 6])
a_dr_cnt_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_burn, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(cnt_burn, condition == 'across' & cold_location == 'dist_rostr')[, 6])
a_pc_cnt_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_burn, condition == 'across' & cold_location == 'prox_caud')[, 5], 
    sd=filter(cnt_burn, condition == 'across' & cold_location == 'prox_caud')[, 6])

# creating rating variable
df$rating <- c(w_dr_tgi_cold, w_pc_tgi_cold, a_dr_tgi_cold, a_pc_tgi_cold, 
               w_dr_cnt_cold, w_pc_cnt_cold, a_dr_cnt_cold, a_pc_cnt_cold,
               w_dr_tgi_warm, w_pc_tgi_warm, a_dr_tgi_warm, a_pc_tgi_warm, 
               w_dr_cnt_warm, w_pc_cnt_warm, a_dr_cnt_warm, a_pc_cnt_warm,
               w_dr_tgi_burn, w_pc_tgi_burn, a_dr_tgi_burn, a_pc_tgi_burn, 
               w_dr_cnt_burn, w_pc_cnt_burn, a_dr_cnt_burn, a_pc_cnt_burn)
return(df)}
```

>>>>

# function to estimate beta parameters from mean and variance
estBetaParams <- function(mu, var) {
     a <- ((1 - mu) / var - 1 / mu) * mu ^ 2
     b <- a * (1 / mu - 1)
     params = c(a,b)
     return(params)
}

@@

# get estimated beta parameters (shape 1 and shape 2) from means and SD
for (c_idx in 1:length(df_sum$manipulation)){
  p <- estBetaParams(df_sum$mean[c_idx], (df_sum$std[c_idx]*df_sum$std[c_idx]))
  df_sum$alpha[c_idx] <- p[1]
  df_sum$beta[c_idx] <- p[2]
}

@@

```{r}
simulate_subj <- function(subid, llim, ulim) {
# trial info
trialN = 12
conditionN = 8
ratingN = 3
# creating simulation data-frame
df <- data.frame(matrix(ncol = 0, nrow = trialN*conditionN*ratingN))
df$id <- rep(subid,trialN*conditionN*ratingN)
df$trialn <- rep(1:trialN,conditionN*ratingN)
df$dermatome <- rep(rep(c(rep("within",trialN*2), rep("across",trialN*2)),2),ratingN)
df$cold_location <- rep(rep(c(rep("dist_rostr",trialN), rep("prox_caud", trialN)),conditionN/2),ratingN)
df$stimuli <- rep(c(rep("tgi",trialN*conditionN/2), rep("non-tgi",trialN*conditionN/2)),ratingN)
df$quality <- c(rep("cold",trialN*conditionN), rep("warm",trialN*conditionN), rep("burn",trialN*conditionN))

# Simulate data here based on means and standard deviations of the above pilot sample
# Cold ratings: simulation
# tgi
w_dr_tgi_cold <- 
  rbeta(
    trialN,
    filter(tgi_cold, condition == 'within' & cold_location == 'dist_rostr')[, 7],
    filter(tgi_cold, condition == 'within' & cold_location == 'dist_rostr')[, 8],
    ncp = 0)
w_pc_tgi_cold <- 
  rbeta(
    trialN,
    filter(tgi_cold, condition == 'within' & cold_location == 'prox_caud')[, 7],
    filter(tgi_cold, condition == 'within' & cold_location == 'prox_caud')[, 8],
    ncp = 0)
a_dr_tgi_cold <- 
  rbeta(
    trialN,
    filter(tgi_cold, condition == 'across' & cold_location == 'dist_rostr')[, 7],
    filter(tgi_cold, condition == 'across' & cold_location == 'dist_rostr')[, 8],
    ncp = 0)
a_pc_tgi_cold <- 
  rbeta(
    trialN,
    filter(tgi_cold, condition == 'across' & cold_location == 'prox_caud')[, 7],
    filter(tgi_cold, condition == 'across' & cold_location == 'prox_caud')[, 8],
    ncp = 0)
# control
w_dr_cnt_cold <- 
  rbeta(
    trialN,
    filter(cnt_cold, condition == 'within' & cold_location == 'dist_rostr')[, 7],
    filter(cnt_cold, condition == 'within' & cold_location == 'dist_rostr')[, 8],
    ncp = 0)
w_pc_cnt_cold <- 
  rbeta(
    trialN,
    filter(cnt_cold, condition == 'within' & cold_location == 'prox_caud')[, 7],
    filter(cnt_cold, condition == 'within' & cold_location == 'prox_caud')[, 8],
    ncp = 0)
a_dr_cnt_cold <- 
  rbeta(
    trialN,
    filter(cnt_cold, condition == 'across' & cold_location == 'dist_rostr')[, 7],
    filter(cnt_cold, condition == 'across' & cold_location == 'dist_rostr')[, 8],
    ncp = 0)
a_pc_cnt_cold <- 
  rbeta(
    trialN,
    filter(cnt_cold, condition == 'across' & cold_location == 'prox_caud')[, 7],
    filter(cnt_cold, condition == 'across' & cold_location == 'prox_caud')[, 8],
    ncp = 0)
# Warm ratings: simulation
# tgi
w_dr_tgi_warm <- 
  rbeta(
    trialN,
    filter(tgi_warm, condition == 'within' & cold_location == 'dist_rostr')[, 7],
    filter(tgi_warm, condition == 'within' & cold_location == 'dist_rostr')[, 8],
    ncp = 0)
w_pc_tgi_warm <- 
  rbeta(
    trialN,
    filter(tgi_warm, condition == 'within' & cold_location == 'prox_caud')[, 7],
    filter(tgi_warm, condition == 'within' & cold_location == 'prox_caud')[, 8],
    ncp = 0)
a_dr_tgi_warm <- 
  rbeta(
    trialN,
    filter(tgi_warm, condition == 'across' & cold_location == 'dist_rostr')[, 7],
    filter(tgi_warm, condition == 'across' & cold_location == 'dist_rostr')[, 8],
    ncp = 0)
a_pc_tgi_warm <- 
  rbeta(
    trialN,
    filter(tgi_warm, condition == 'across' & cold_location == 'prox_caud')[, 7],
    filter(tgi_warm, condition == 'across' & cold_location == 'prox_caud')[, 8],
    ncp = 0)
# control
w_dr_cnt_warm <- 
  rbeta(
    trialN,
    filter(cnt_warm, condition == 'within' & cold_location == 'dist_rostr')[, 7],
    filter(cnt_warm, condition == 'within' & cold_location == 'dist_rostr')[, 8],
    ncp = 0)
w_pc_cnt_warm <- 
  rbeta(
    trialN,
    filter(cnt_warm, condition == 'within' & cold_location == 'prox_caud')[, 7],
    filter(cnt_warm, condition == 'within' & cold_location == 'prox_caud')[, 8],
    ncp = 0)
a_dr_cnt_warm <- 
  rbeta(
    trialN,
    filter(cnt_warm, condition == 'across' & cold_location == 'dist_rostr')[, 7],
    filter(cnt_warm, condition == 'across' & cold_location == 'dist_rostr')[, 8],
    ncp = 0)
a_pc_cnt_warm <- 
  rbeta(
    trialN,
    filter(cnt_warm, condition == 'across' & cold_location == 'prox_caud')[, 7],
    filter(cnt_warm, condition == 'across' & cold_location == 'prox_caud')[, 8],
    ncp = 0)
# burn
w_dr_tgi_burn <- 
  rbeta(
    trialN,
    filter(tgi_burn, condition == 'within' & cold_location == 'dist_rostr')[, 7],
    filter(tgi_burn, condition == 'within' & cold_location == 'dist_rostr')[, 8],
    ncp = 0)
w_pc_tgi_burn <- 
  rbeta(
    trialN,
    filter(tgi_burn, condition == 'within' & cold_location == 'prox_caud')[, 7],
    filter(tgi_burn, condition == 'within' & cold_location == 'prox_caud')[, 8],
    ncp = 0)
a_dr_tgi_burn <- 
  rbeta(
    trialN,
    filter(tgi_burn, condition == 'across' & cold_location == 'dist_rostr')[, 7],
    filter(tgi_burn, condition == 'across' & cold_location == 'dist_rostr')[, 8],
    ncp = 0)
a_pc_tgi_burn <- 
  rbeta(
    trialN,
    filter(tgi_burn, condition == 'across' & cold_location == 'prox_caud')[, 7],
    filter(tgi_burn, condition == 'across' & cold_location == 'prox_caud')[, 8],
    ncp = 0)
# control
w_dr_cnt_burn <- 
  rbeta(
    trialN,
    filter(cnt_burn, condition == 'within' & cold_location == 'dist_rostr')[, 7],
    filter(cnt_burn, condition == 'within' & cold_location == 'dist_rostr')[, 8],
    ncp = 0)
w_pc_cnt_burn <- 
  rbeta(
    trialN,
    filter(cnt_burn, condition == 'within' & cold_location == 'prox_caud')[, 7],
    filter(cnt_burn, condition == 'within' & cold_location == 'prox_caud')[, 8],
    ncp = 0)
a_dr_cnt_burn <- 
  rbeta(
    trialN,
    filter(cnt_burn, condition == 'across' & cold_location == 'dist_rostr')[, 7],
    filter(cnt_burn, condition == 'across' & cold_location == 'dist_rostr')[, 8],
    ncp = 0)
a_pc_cnt_burn <- 
  rbeta(
    trialN,
    filter(cnt_burn, condition == 'across' & cold_location == 'prox_caud')[, 7],
    filter(cnt_burn, condition == 'across' & cold_location == 'prox_caud')[, 8],
    ncp = 0)

# creating rating variable
df$rating <- c(w_dr_tgi_cold, w_pc_tgi_cold, a_dr_tgi_cold, a_pc_tgi_cold, 
               w_dr_cnt_cold, w_pc_cnt_cold, a_dr_cnt_cold, a_pc_cnt_cold,
               w_dr_tgi_warm, w_pc_tgi_warm, a_dr_tgi_warm, a_pc_tgi_warm, 
               w_dr_cnt_warm, w_pc_cnt_warm, a_dr_cnt_warm, a_pc_cnt_warm,
               w_dr_tgi_burn, w_pc_tgi_burn, a_dr_tgi_burn, a_pc_tgi_burn, 
               w_dr_cnt_burn, w_pc_cnt_burn, a_dr_cnt_burn, a_pc_cnt_burn)

return(df)}
```
